Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-17 WSSSPE3/report/wg_main_publishing_SW.tex
minor changes/comments in publishing sections moved some credit text to be a general intro to the section
minor change to start of publishing section
Section 5.9: No content change.
Section 5.9:  teeny-weeny transformation

\subsubsection{Why it is important}

This group explored the value of executable papers (papers whose content
includes the code needed to produce their own results), and other forms of
publishing which include dynamic electronic content. Transitioning to this type
of publication offers possibilities of addressing, or partially addressing
sustainability concerns such as reproducibility, software credit, and best
practices.

@@

\textbf{Reproducibility}: Part of the purpose of these executable paper venues
is to (at least partially) address the reproducibility issue by making the
paper itself recompute its own results.

@@

\textbf{Best Practices (\S\ref{sec:best-practices})}: Because an executable paper
showcases the code, and the code itself is subject to the review process,
authors are more likely to pay attention to coding practices. In addition,
because the paper must explain what the code does, better documentation is
likely to be achieved.

@@

@@

The plan is to create a web page describing executable papers, their value, and
a list of what publishers support them.

@@

The aforementioned page to be published on SSI.

>>>>

This group explored the value of executable papers (papers whose content
includes the code needed to produce their own results), and other forms of
publishing which include dynamic electronic content.
%
%\subsubsection{Why it is important}
%
Transitioning to this type of publication offers possibilities of addressing, or
partially addressing, sustainability concerns such as reproducibility, software
credit, and best practices.

@@

\textbf{Reproducibility}: Part of the purpose of these executable paper venues
is to (at least partially) address the reproducibility issue by making a paper
itself recompute its own results.

@@

\textbf{Best Practices (\S\ref{sec:best-practices})}: Because an executable
paper showcases the code, and the code itself is subject to the review process,
authors are more likely to pay attention to coding practices. In addition,
because the paper must explain what the code does, better documentation is
more likely to be achieved.

@@

See Appendix~\ref{sec:appendix_publishing_SW} for more details about the
discussion.

@@

The plan is to create a web page describing executable papers, their values, and
a list of what publishers support them. \katznote{when?}

@@

The aforementioned page will be published on the Software Sustainability
Institute website: \url{http://www.software.ac.uk}.
